Results MSRC latent class analysis

### 2021-02-15 codebook_df.Rmd
Analyses first draft
exclude participants for whom it's unclear whether they are currently serving

---
title: "Codebook created on 2021-02-06 at 2021-02-06 11:35:18"
output: github_document
---

@@

## Dataset description
The data contains 2648 cases and 25 variables.

>>>>

---
title: "Codebook created on 2021-02-15 at 2021-02-15 10:15:54"
output: github_document
---

@@

## Dataset description
The data contains 2411 cases and 25 variables.

### 2021-02-15 manuscript/manuscript.Rmd
exclude participants for whom it's unclear whether they are currently serving

```{r}
library(ggplot2)
library(tidySEM)
library(tidyLPA)
load_data()
desc <- descriptives(df)
# We're aiming to characterize profiles/classes based on the characteristics of suicide attempts (CDE7_NEW, CDE8, CDE9, CDE10, CDE11, CDE12, CDE13, CDE17).

>>>>

```{r}
library(ggplot2)
library(tidySEM)
library(tidyLPA)
load_data()

desc <- descriptives(df)
# We're aiming to characterize profiles/classes based on the characteristics of suicide attempts (CDE7_NEW, CDE8, CDE9, CDE10, CDE11, CDE12, CDE13, CDE17).
